---
title: "DS 202 Lab 2"
author: "Bernard Fay; GitHub: bj99fay"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

The ratings tend to fall between 2.5 and 4. Additionally, the shappe looks close to normal; the differences are likely due to the subjective way the chocolates are rated. There are at least two outliers, one with a rating of 1 and another with a rating of 5.

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
ggplot(data=choco, aes(x=Rating,)) + 
    geom_bar(fill = "blue", colour = "black")+
    theme_bw()+
    theme(axis.title.y = element_text(size = rel(1)),
          axis.title.x = element_text(size = rel(1)),
          axis.text.x = element_text(size = rel(1)),
          axis.text.y = element_text(size = rel(1)),
          plot.title = element_text(hjust=0.5, size = rel(1.5)))+
    labs(x = "Rating",
         y = "Count",
         title = "Chocolate Ratings")
```

There doesn't appear to be a strong correlation bewteen Rating and Cocoa Percent. If there is a correlation, ut would be slightly negative, meaning as the Rating increases, the Cocoa Percent decreases.

```{r}
ggplot(data=choco, aes(x=Rating, y=Cocoa.Pct, group=1)) + 
    geom_point()+
    theme_bw()+
    theme(axis.title.y = element_text(size = rel(1)),
          axis.title.x = element_text(size = rel(1)),
          axis.text.x = element_text(size = rel(1)),
          axis.text.y = element_text(size = rel(1)),
          plot.title = element_text(hjust=0.5, size = rel(1.5)))+
    labs(x = "Rating",
         y = "Cocoa Percent",
         title = "Chocolate Ratings")
```
