---
title: "Collaborative Portion"
author: "Bernard Fay; Github: ; Chase Weida; Github: cweida"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
choco <- read.csv('https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv')
```

#### 1. Overall number of chocolate bars?
```{r}
length(choco$Rating)
```

There are 1852 unique chocolate bars tested and rated.


#### 2. How does the number of ratings depend on the year?
```{r}
hist(choco$Review.Date, breaks = seq(2005.5, 2017.5, by = 1))
```

As you can see, that the ratings slowly increased over the years until 2015, but fell a bit in 2016 and much more greatly in 2017.

#### 3. What are the three locations with the most ratings? How do ratings compare across these company locations?

```{r}
tbl <- table(choco$Company.Location)
df <- tbl[order(-as.numeric(tbl))]
df[1:3]

US <- choco[choco$Company.Location == "U.S.A.", ]
USmean <- mean(US[,"Rating"])
names(USmean) <- "U.S.A. mean"

France <- choco[choco$Company.Location == "France", ]
FranceMean <- mean(France[,"Rating"])
names(FranceMean) <- "France mean"

Canada <- choco[choco$Company.Location == "Canada", ]
CanadaMean <- mean(Canada[,"Rating"])
names(CanadaMean) <- "Canada mean"

c(USmean, FranceMean, CanadaMean)
```

The USA, France, and Canada have the most ratings. Surprisingly, the ratings go in the reverse order with Canada at the top followed by France and the USA.

#### 4. Ask an interesting question.

Do ratings depend on company location?

#### 5. Answer the question you came up with in question 4

```{r}
df <- choco[, c("Company.Location", "Rating")]
head(df)

df2 <- aggregate(df[, 2], list(df$Company.Location), mean)
names(df2)[names(df2) == "Group.1"] <- "Company.Location"
names(df2)[names(df2) == "x"] <- "Rating"
df2 <- df2[order(-df2$Rating),]
barplot(df2$Rating, main='Rating by Company Location', ylab='Rating', xlab='Company Location', names.arg=df2$Company.Location)
```

There appears to be a negative correlation between company location and ratings. The average rating is not the same for each country, indicating that the company location influences the rating for the chocolate. Exactly why that is can not be determined from the available data.

#### 6. Describe the workflow.
