---
title: "Collaborative Portion"
author: "Bernard Fay; Github: ; Chase Weida; Github: cweida"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
choco <- read.csv('https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv')
```

#### 1. Overall number of chocolate bars?
```{r}
length(choco$Rating)
```

There are 1852 unique chocolate bars tested and rated.


#### 2. How does the number of ratings depend on the year?
```{r}
hist(choco$Review.Date, breaks = seq(2005.5, 2017.5, by = 1))
```

As you can see, that the ratings slowly increased over the years until 2015, but fell a bit in 2016 and much more greatly in 2017.

#### 3. What are the three locations with the most ratings? How do ratings compare across these company locations?

```{r}
tbl <- table(choco$Company.Location)
df <- tbl[order(-as.numeric(tbl))]
df[1:3]

US <- choco[choco$Company.Location == "U.S.A.", ]
USmean <- mean(US[,"Rating"])
names(USmean) <- "U.S.A. mean"

France <- choco[choco$Company.Location == "France", ]
FranceMean <- mean(France[,"Rating"])
names(FranceMean) <- "France mean"

Canada <- choco[choco$Company.Location == "Canada", ]
CanadaMean <- mean(Canada[,"Rating"])
names(CanadaMean) <- "Canada mean"

c(USmean, FranceMean, CanadaMean)
```

The USA, France, and Canada have the most ratings. Surprisingly, the ratings go in the reverse order with Canada at the top followed by France and the USA.
